Approximation as Differentiation

### 2025-05-06 appendix/notes.tex
Rename.

Covered so far:
\begin{itemize}
\item automatic differentiation (\secref{auto-diff})
\item $\CMon$-enriched categories, including enriched functors and enriched Yoneda embedding (\secref{cmon-enriched})
\item biproducts and semi-additive categories (\secref{biproduct})
\item useful semi-additive categories (\secref{useful-semi-additive-categories}):
   \begin{itemize}
   \item category $\LatGal$ of bounded lattices and Galois connections (\secref{categories-with-biproducts:latgal})
   \item category $\FinVect_F$ of finite-dimensional vector spaces over a field $F$
   (\secref{categories-with-biproducts:fdvect})
   \end{itemize}
\item category $\Fam(I,\cat{C})$ of $I$-indexed families of objects of $\cat{C}$ (\secref{fam})
\item set-indexed products (\secref{set-indexed-product})
\item Grothendieck construction $\Grothendieck{\cat{C}}F$ and category of families $\Fam(\cat{C})$
(\secref{grothendieck})
\item useful categories of families for automatic approximation
(\secref{galois-slicing-auto-diff-via-grothendieck}):
   \begin{itemize}
      \item Galois slicing via $\Fam(\LatGal)$ (\secref{galois-slicing-auto-diff-via-grothendieck:galois-slicing})
      \item automatic differentiation via $\Fam(\FinVect)$ (\secref{galois-slicing-auto-diff-via-grothendieck:auto-diff})
   \end{itemize}
\end{itemize}

@@

\input{appendix/notes/preliminaries}
\input{appendix/notes/auto-diff}
\input{appendix/notes/cmon}
\input{appendix/notes/cmon-enriched}
\input{appendix/notes/biproduct}
\input{appendix/notes/useful-semi-additive-categories}
\input{appendix/notes/fam}
\input{appendix/notes/set-indexed-product}
\input{appendix/notes/grothendieck}
\input{appendix/notes/auto-diff-galois-slicing-via-grothendieck}
\input{appendix/notes/language}

>>>>

Covered so far:
\begin{itemize}
\item automatic differentiation (\secref{auto-diff})
\item $\CMon$-enriched categories, including enriched functors and enriched Yoneda embedding (\secref{cmon-enriched})
\item biproducts and semi-additive categories (\secref{biproduct})
\item useful semi-additive categories (\secref{useful-semi-additive-categories}):
   \begin{itemize}
   \item category $\LatGal$ of bounded lattices and Galois connections (\secref{categories-with-biproducts:latgal})
   \item category $\FinVect_F$ of finite-dimensional vector spaces over a field $F$
   (\secref{categories-with-biproducts:fdvect})
   \end{itemize}
\item category $\Fam(I,\cat{C})$ of $I$-indexed families of objects of $\cat{C}$ (\secref{fam})
\item set-indexed products (\secref{set-indexed-product})
\item Grothendieck construction $\Grothendieck{\cat{C}}F$ and category of families $\Fam(\cat{C})$
(\secref{grothendieck})
\item useful categories of families for automatic approximation
(\secref{galois-slicing-auto-diff-via-fam}):
   \begin{itemize}
      \item Galois slicing via $\Fam(\LatGal)$ (\secref{galois-slicing-auto-diff-via-fam:galois-slicing})
      \item automatic differentiation via $\Fam(\FinVect)$ (\secref{galois-slicing-auto-diff-via-fam:auto-diff})
   \end{itemize}
\end{itemize}

@@

\input{appendix/notes/preliminaries}
\input{appendix/notes/auto-diff}
\input{appendix/notes/cmon}
\input{appendix/notes/cmon-enriched}
\input{appendix/notes/biproduct}
\input{appendix/notes/useful-semi-additive-categories}
\input{appendix/notes/fam}
\input{appendix/notes/set-indexed-product}
\input{appendix/notes/grothendieck}
\input{appendix/notes/auto-diff-galois-slicing-via-fam}
\input{appendix/notes/language}

### 2025-05-06 appendix/notes/auto-diff-galois-slicing-via-fam.tex
Rename.

\subsection{Galois slicing and automatic differentiation via Grothendieck construction}
\label{sec:galois-slicing-auto-diff-via-grothendieck}

\subsubsection{Galois slicing via a category of families}
\label{sec:galois-slicing-auto-diff-via-grothendieck:galois-slicing}

@@

\subsubsection{Automatic differentiation via categories of families}
\label{sec:galois-slicing-auto-diff-via-grothendieck:auto-diff}

Recall that $\Fam(\FinVect)$ denotes the Grothendieck construction $\Grothendieck{X}\Fam(X, \FinVect)$. The
functor $\Diff \hookrightarrow \Fam(\FinVect)$ which send objects $\RR^n$ to constant families of tangent
spaces $(\RR^n, \const(\RR^n))$ and morphisms $f: \RR^m \to \RR^n \times (\RR^m \linearto \RR^n)$ to pairs
$(f_1, f_2)$ of differentiable functions $f_1: \RR^m \to \RR^n$ and families of linear maps $f_2: \{{f_2}_x:
\RR^m \linearto \RR^n\}_{x \in \RR^m}$ exhibits $\Diff$ as equivalent to a full subcategory of
$\Fam(\FinVect)$.

For any $(f, \partial f): (\RR^m, \const(\RR^m)) \to (\RR^n, \const(\RR^n))$ and $(g, \partial g): (\RR^n,
\const(\RR^n)) \to (\RR^k, \const(\RR^k))$ in that subcategory, we have that for any $x \in \RR^m$:
\begin{itemize}
\item $\partial f_x: \RR^m \to \RR^n$;
\item $\reindex{\partial g}{f}_x = \partial g_{f(x)}: \RR^n \to \RR^k$.
\end{itemize}

>>>>

\subsection{Galois slicing and automatic differentiation via categories of families}
\label{sec:galois-slicing-auto-diff-via-fam}

\subsubsection{Galois slicing}
\label{sec:galois-slicing-auto-diff-via-fam:galois-slicing}

@@

\subsubsection{Automatic differentiation}
\label{sec:galois-slicing-auto-diff-via-fam:auto-diff}

Recall that $\Fam(\FinVect)$ denotes the Grothendieck construction $\Grothendieck{X}\Fam(X, \FinVect)$.
Consider the functor $\Diff \hookrightarrow \Fam(\FinVect)$ which send objects $\RR^n$ to constant families of
tangent spaces $(\RR^n, \const(\RR^n))$ and morphisms $f: \RR^m \to \RR^n \times (\RR^m \linearto \RR^n)$ to
pairs $(f_1, f_2)$ of differentiable functions $f_1: \RR^m \to \RR^n$ and families of linear maps $f_2:
\{{f_2}_x: \RR^m \linearto \RR^n\}_{x \in \RR^m}$. This exhibits $\Diff$ as equivalent to a full subcategory
of $\Fam(\FinVect)$.

In that subcategory, for any $(f, \partial f): (\RR^m, \const(\RR^m)) \to (\RR^n, \const(\RR^n))$ and $(g,
\partial g): (\RR^n, \const(\RR^n)) \to (\RR^k, \const(\RR^k))$, we have that for any $x \in \RR^m$:
\begin{itemize}
\item $\partial f_x: \RR^m \to \RR^n$;
\item $\reindex{\partial g}{f}_x = \partial g_{f(x)}: \RR^n \to \RR^k$.
\end{itemize}
